---
title: "Link Prediction lastFM"
author: "Emma Perez, Andrés Camargo"
date: "2023-05-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Packages needed

```{r}
library(tidyverse)
library(igraph)
library(visNetwork)
library(ggplot2)
library(ggthemes)
library(caret)
set.seed(123)

```


## 0. Network description

*LastFM Asia Social Network*

The chosen network is a social network of LastFM Asian users available at the [Stanford Network Analysis Platform (SNAP)](https://snap.stanford.edu/index.html). Last.fm is a social media, an internet radio, and also a music recommendation system that builds profiles and statistics about musical preferences, based on data sent by registered users.

According to SNAP, the data was collected from the public API in March 2020. Nodes are LastFM users from Asian countries and edges are mutual follower relationships between them. The vertex features are extracted based on the artists liked by the users. It can be downloaded in csv format from [LastFM Asia Social Network](https://snap.stanford.edu/data/feather-lastfm-social.html). 

The network will be used to perform link prediction. 

To start with, the data is loaded to R. 


```{r}
fm = read_delim("lasftm_asia/lastfm_asia_edges.csv", delim=",")
g = graph.data.frame(fm, directed = FALSE)
```

```{r}
g
plot(g)
```
The network has 7624 edges and 27806 links. 

```{r}
par(mar=c(0,0,0,0),mfrow=c(1,3))
E(g)$color<-"lightgray"; V(g)$color <- "white";ll <- layout.kamada.kawai(g)
plot(g,layout=ll,vertex.label="", vertex.size = 1)

```

## 1. Edges deletion

*Delete a fraction of real edges in the network and create a table of those links deleted (positive class) and of links non-present (negative class) *


```{r}
set.seed(123)
nlinks <- 1600
ii <- sample(1:ecount(g),nlinks)
gp <- delete_edges(g,ii)
```

Table of deleted (true) links
```{r}
true_edges <- data.frame(get.edges(g,ii))
true_edges
```

Table of false links

```{r}
false_edges <- data.frame()
most_connected <- which(degree(g)>10)
for(i in 1:nlinks){
  i1 <- sample(most_connected,1)
  i2 <- sample(most_connected,1)
  if(!are.connected(g,i1,i2)) false_edges <- rbind(false_edges,data.frame(X1=i1,X2=i2))
}

false_edges
```


##2. Similarity metrics

*Generate a number of proximity/similarty metrics heuristics for each link in the positive and negative class*

```{r}
true_edges <- data.frame(true_edges,obs=1)  
false_edges <- data.frame(false_edges,obs=0)

total_edges <- rbind(true_edges,false_edges)
colnames(total_edges) <- c("id1","id2","obs")
```


```{r}

n1 <- neighborhood(gp,order=1,nodes=total_edges$id1)
head(n1)
n2 <- neighborhood(gp,order=1,nodes=total_edges$id2)
head(n2)
```

```{r}
total_edges$sim_jacc <- 0
total_edges$sim_aa <- 0
total_edges$sim_pref <- 0
for(i in 1:nrow(total_edges)){
   common_neigh <- intersect(n1[[i]],n2[[i]])
   all_neigh <- union(n1[[i]],n2[[i]])
   degree_common_neigh <- degree(gp,common_neigh)
   total_edges$sim_jacc[i] <- length(common_neigh)/(length(all_neigh)-2)
   if(length(common_neigh)>0) total_edges$sim_aa[i] <- sum(1/log(degree_common_neigh))
   total_edges$sim_pref[i] <- length(n1[[i]])*length(n2[[i]])
}

total_edges
```

```{r}
total_edges %>% pivot_longer(c(sim_jacc,sim_aa,sim_pref)) %>%
  ggplot(aes(x=as.factor(obs),y=value)) + geom_boxplot() + facet_wrap(~name,scales="free")
```

```{r}
ii <- sample(1:nrow(total_edges),0.75*nrow(total_edges))
total_edges_train <- total_edges[ii,]
total_edges_test <- total_edges[-ii,]
```


##3. Binary classifier training 

*Train a binary classifier to predict the links, i.e., to predict the class (positive/negative) using those heuristics. Use crossvalidation.*


```{r}
require(stargazer)
glm_link <- glm(obs ~ sim_jacc+sim_aa+sim_pref,
                data=total_edges_train,family=binomial(link="logit"))

library(stargazer)
stargazer(glm_link,type = "text",single.row = T,header=FALSE)
```

```{r}
glm_prediction <- predict.glm(glm_link,total_edges_test,type="response") 
```

```{r}
pred <- sign(glm_prediction > 0.3)

table(pred,total_edges_test$obs,dnn=c("pred","obs"))
```

##4. Model evaluation

*Evaluate the precision of the model. Which heuristic is the most important. Why do you think it is the most important?*


```{r}
confusionMatrix(factor(pred),factor(total_edges_test$obs),positive = "1")
```


### Training Using Cross Validation

```{r}
total_edges_train = total_edges_train %>% mutate(obs = as.factor(obs))
total_edges_test = total_edges_test %>% mutate(obs = as.factor(obs))
levels(total_edges_train$obs)= c("No","Yes")
levels(total_edges_test$obs)= c("No","Yes")

ctrl = trainControl(
  method = "repeatedcv",
  number = 10,
  classProbs = T,
  summaryFunction = twoClassSummary,
  verboseIter = T
  )

rfFit = train(
  obs ~ sim_jacc+sim_aa+sim_pref,
  data = total_edges_train,
  method= "rf",
  preProc= c('scale', 'center'),
  tuneLength= 10,
  metric = "ROC",
  trControl = ctrl
)

rfProb = predict(rfFit, total_edges_test, type = "prob")
prediction = as.factor(ifelse(rfProb[,2]>0.1, "Yes", "No"))

confusionMatrix(prediction, total_edges_test$obs)


```





```{r}
varImp(glm_link)
```

```{r}
require(corrplot)
cc <- cor(total_edges_test[,c("sim_jacc","sim_aa","sim_pref")])
corrplot(cc)
```

##5. Potential improvements 

*Comment on potential ways to improve the link prediction* 

