---
title: "Link Prediction lastFM"
author: "Emma Perez, Andrés Camargo"
date: "2023-05-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Packages needed

```{r}
library(tidyverse)
library(igraph)
library(visNetwork)
library(ggplot2)
library(ggthemes)

```


## 0. Network description

```{r}
fm = read_delim("lasftm_asia/lastfm_asia_edges.csv", delim=",")
g = graph.data.frame(fm, directed = FALSE)
g
plot(g)
```

```{r}
par(mar=c(0,0,0,0),mfrow=c(1,3))
E(g)$color<-"lightgray"; V(g)$color <- "white";ll <- layout.kamada.kawai(g)
plot(g,layout=ll,vertex.label="")
ierase = get.edge.ids(g, c(1,18))
E(g)$color[ierase] = "red"
plot(g,layout=ll,vertex.label="")
V(g)$color[c(20,34)] <- "orange"
plot(delete_edges(g,ierase),layout=ll,vertex.label="")


```

## 1. Edges deletion

*Delete a fraction of real edges in the network and create a table of those links deleted (positive class) and of links non-present (negative class) *


##2. Similarity metrics

*Generate a number of proximity/similarty metrics heuristics for each link in the positive and negative class*


##3. Binary classifier training 

*Train a binary classifier to predict the links, i.e., to predict the class (positive/negative) using those heuristics. Use crossvalidation.*

##4. Model evaluation

*Evaluate the precision of the model. Which heuristic is the most important. Why do you think it is the most important?*

##5. Potential improvements 

*Comment on potential ways to improve the link prediction* 
