---
title: "Final Assignment"
author: "Emma Pérez & Andrés Camargo"
date: "2023-05-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries

```{r}
library(tidyverse)
library(igraph)
library(visNetwork)
library(ggplot2)
library(ggthemes)
library(caret)
set.seed(123)

```


## 0. Network 

*LastFM Asia Social Network*

We will continue working with the social network of LastFM Asian users, which is available at the [Stanford Network Analysis Platform (SNAP)](https://snap.stanford.edu/index.html). Last.fm is a social media, an internet radio, and also a music recommendation system that builds profiles and statistics about musical preferences, based on data sent by registered users.

According to SNAP, the data was collected from the public API in March 2020. Nodes are LastFM users from Asian countries and edges are mutual follower relationships between them. The vertex features are extracted based on the artists liked by the users. It can be downloaded in csv format from [LastFM Asia Social Network](https://snap.stanford.edu/data/feather-lastfm-social.html). 

To start with, the data is loaded to R. 

```{r}
fm = read_delim("lasftm_asia/lastfm_asia_edges.csv", delim=",")
g = graph.data.frame(fm, directed = FALSE)
```

```{r}
sim_sir <- function(g,beta,mu,seeds){
  state <- rep(0,vcount(g)) #initial state of the simulation
  state[seeds] <- 1 #infect the seeds
  t <- 0
  table <- data.frame(t=0,inf=seeds)
  while(sum(state==1)>0){
    t <- t + 1
    #I -> R
    infected <- which(state==1)
    state[infected] <- ifelse(runif(length(infected)) < mu,2,1)
    
    #S -> I
    infected <- which(state==1)
    susceptible <- which(state==0) #get them
    contacts <- as.numeric(unlist(adjacent_vertices(g,infected))) #get the contacts of infected
    contacts <- contacts[contacts %in% susceptible]
    new_infected <- contacts[runif(length(contacts)) < beta] #infect contacts
    if(length(new_infected)>0){
      state[new_infected] <- 1
      table <- rbind(table,data.frame(t,inf=new_infected))
    }
  }
  table
}
```


```
# small realization
 
seeds <- sample(1:vcount(g),1)
realization <- sim_sir(g,beta = 0.5,mu=0.1,seeds) 
realization

# big realization

seeds <- sample(1:vcount(g),vcount(g)*0.01)
realization <- sim_sir(g,beta = 0.5,mu=0.1,seeds) 
```

Propagation

```
par(mar=c(0,0,0,0),mfrow=c(1,3))
ll <- layout.kamada.kawai(g)
V(g)$tfin <- 1e100; V(g)$tinf[realization$inf] <- realization$t
plot(g,layout=ll,vertex.label="",
     vertex.color=ifelse(V(g)$tinf <= 0,"red","lightblue"),vertex.size=4)
plot(g,layout=ll,vertex.label="",
     vertex.color=ifelse(V(g)$tinf <= 5,"red","lightblue"),vertex.size=4)
plot(g,layout=ll,vertex.label="",
     vertex.color=ifelse(V(g)$tinf <= 10,"red","lightblue"),vertex.size=4)
```

Infection Curve

```
realization <- sim_sir(g,beta = 0.5,mu=0.1,seeds) %>% 
  group_by(t) %>% summarize(ninf=n()) 
realization %>% 
  ggplot(aes(x=t,y=ninf)) + geom_line()
```

## 1. Epidemic threshold

*Find the theoretical epidemic threshold βc for your network for the information
to reach a significant number of nodes.*

```{r}

```


## 2. SIR simulation

*Assuming that randomly-selected 1% of the nodes of your network knows
about the information, simulate the SIR model below and above that threshold
and plot the number of infected people as a function of β.*

```{r}

```


## 3. Acelerate Infection

*Choose a β above βc. Using centrality, communities or any other metric, find
a better set of 1% of seeds in the network so we get more infected people
than the random case. Measure the difference of your choice with the random
case as:*

- The difference in the total number of infected people
- The difference in the time of the peak of infection (when most infections
happen).

```{r}

```


## 4. Inmunization

*Suppose now that you can convince 5% of people in the network not to
spread that information at all:*

- Choose those 5% randomly in the network. Simulate the SIR model above
βc using 1% of the remaining nodes as seeds. Choose those seeds
randomly.
- Choose those 5% according to their centrality. Simulate the SIR model
above βc using 1% of the remaining nodes as seeds. Choose those seeds
randomly.
- Measure the difference between both cases as you did in part c).

```{r}

```


## 5. Analysis of Inmunization

*Comment on the relationship between the nodes you found in part c) and d)
using the same type of centrality. Are they related or completely different?*

```{r}

```


## 6. Improve inmunization

*With the results of part b) train a model that predicts that time to infection of a
node using their degree, centrality, betweeness and page rank. Use that
model to select the seed nodes as those with the smallest time to infection in
part c).*

```{r}

```


## Repeat d).

```{r}

```

